{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2021-03-05 documents/experiment_1_data.tex
More work on writing, need to add pulse counts

\subsection{Data from testing on bacteriophage T4}
\begin{table}[h!]
	\centering
	\begin{tabular}{ |c|c|c|c| } 
				\hline
		\multicolumn{3}{|c|}{\textbf{Calibration trials} } \\
		\hline
		\hline
		Exposure & kilocounts per 10s integration & Note \# \\
		\hline
		Autoclaved phage (0.2 mL) & 30 & \\ 
		Autoclaved p. (50 uL) & 32 & Run 8\\ 
		\hline
		Phage culture 'blank' & 8 & \\ 
		Water & 1 & \\

@@

		\hline
		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, 10 or 20 us CW pulses 84.8 V/m pessimistic to 339 V/m optimistic} \\
		\hline
		Sham   & 12 & Run 8 t4,5...\\
		+ & 11 & Run 8 t4,5...\\
		+  & 12 & Run 8 t4,5...\\
		+  & 12 & Run 8 t4,5...\\
		\hline
		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, phage degraded with basic buffer, 84.8 V/m pessimistic to 339 V/m optimistic} \\
		\hline
		Blank (0 min) & 14 & Run 9 \\
		Blank (\ntilde 15 min) & 17 & Run 9\\
		Sham (\ntilde 15 min) & 5 & Run 9\\
		Blank (\ntilde 4 hr) & 24 & Run 9\\
		\hline
		+  & 14 & Run 11\\
		Sham & 17 & Run 11\\
		\hline
		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, 10 or 20 us CW pulses, 84.8 V/m pessimistic to 339 V/m optimistic} \\
		\hline
		Sham & 12 & Run 12\\
		+    & 10 & Run 12\\
		\hline
		\multicolumn{3}{|c|}{\textbf{0.2 mm channel}, 6 to 12 GHz, 10 or 20 us CW pulses, 200 V/m pes. and 10.6 kV/m opt.} \\
		\hline
		 Sham & 12 & CPWG micro-\\
 		 +    & 10 & CPWG micro-\\

@@

		\multicolumn{3}{|c|}{\ntilde 0.03 mm channel, basic buffer, tainted as pH may not have been 10.6, 1 MV/m to 38 MV/m} \\
		\hline
		Sham & 12 & Weakened \\ 
		Blank & 11 & Weakened  \\ 
		Blank & 12 & Weakened  \\ 
		Blank & 9 & Weakened  \\ 
		+ & 11 & Weakened \\
		+ (no term) & 11 & Weakened \\ 
		+ & 9 & Weakened \\ 
		\hline
	\end{tabular}
\end{table}

>>>>

\subsection{Data from testing on bacteriophage T4}

\begin{table}[h!]
	\centering
	\begin{tabular}{ |c|c|c|c| } 
				\hline
		\multicolumn{3}{|c|}{\textbf{Calibration trials} } \\
		\hline
		\hline
		Exposure & kilocounts per 10s integration & Note \# \\
		\hline
		Autoclaved phage (0.2 mL) & 30 & \\ 
		Autoclaved p. (50 uL) & 32 & Run 8\\ 
		\hline
		Phage culture 'blank' & 8 & \\ 
		Water & 1 & \\

@@

		\hline
		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, 10 or 20 us CW pulses, 84.8 V/m to 339 V/m} \\
		\hline
		Sham   & 12 & Run 8 t4,5...\\
		+ & 11 & Run 8 t4,5...\\
		+  & 12 & Run 8 t4,5...\\
		+  & 12 & Run 8 t4,5...\\
		\hline
		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, phage degraded with basic buffer, 84.8 V/m to 339 V/m} \\
		\hline
		Blank (0 min) & 14 & Run 9 \\
		Blank (\ntilde 15 min) & 17 & Run 9\\
		Sham (\ntilde 15 min) & 5 & Run 9\\
		Blank (\ntilde 4 hr) & 24 & Run 9\\
		\hline
		+  & 14 & Run 11\\
		Sham & 17 & Run 11\\
		\hline
		\multicolumn{3}{|c|}{\textbf{NF capillary}, 6 to 12 GHz, 10 or 20 us CW pulses, 84.8 V/m to 339 V/m} \\
		\hline
		Sham & 12 & Run 12\\
		+    & 10 & Run 12\\
		\hline
		\multicolumn{3}{|c|}{\textbf{0.2 mm channel}, 6 to 12 GHz, 10 or 20 us CW pulses, 200 V/m pes. and 10.6 kV/m opt.} \\
		\hline
		 Sham & 12 & CPWG micro-\\
 		 +    & 10 & CPWG micro-\\

@@

		\multicolumn{3}{|c|}{\ntilde 0.03 mm channel, basic buffer, tainted as pH may not have been 10.6, 1 MV/m to 38 MV/m} \\
		\hline
		Sham & 12 & Weakened \\  
		Blank & 11 & Weakened  \\ 
		Blank & 12 & Weakened  \\ 
		Blank & 9 & Weakened  \\ 
		+ & 11 & Weakened \\
		+ (no term) & 11 & Weakened \\ 
		+ & 9 & Weakened \\ 
		\hline
	\end{tabular}
\end{table}
%how many counts?

Note the width of the electric field error bars. These are not meaningful random or systematic intervals; while we have tried to do our best with the instruments available, we cannot confidently assert that the field was within this range.

### 2021-03-05 documents/summary.tex
More work on writing, need to add pulse counts

\begin{figure}[H]
%\captionsetup{singlelinecheck = false, justification=justified}
	\centering

	\subfloat[]{
		\includegraphics*[width=0.5\textwidth]{pulse_exposure_setup.JPG}
	}
	\subfloat[]{
		\includegraphics*[width=0.5\textwidth]{eppenwolf_2.jpg}
	}
    \hfill
	\subfloat[]{
		\includegraphics*[width=0.5\textwidth]{bronch_9GHz_500W_2_transparent.png}
	}
	\subfloat[]{
		\includegraphics*[width=0.5\textwidth]{CPWG_sim_pretty_2}
	}
    \hfill

	\subfloat[]{
		\includegraphics[width=0.3\textwidth]{x_gal.jpg}
	}
	\subfloat[]{
		\includegraphics[width=0.5\textwidth]{fluro_1}
	}
%	\caption{Simulation of a (largely ineffective) bronchoscopic method.}
%	\caption{\\ \textit{Chengxiang} nanosecond pulse exposure jig. Pulser seen off the left. Pulse shaping plate not shown. Aluminum disc belongs to the scan-conversion digitizer, not used in this study.}
%		\caption{\\ \textit{Eppenwolf} misguided pulsed X-Band microwave spectrometer used in this study. (cuvette shown was replaced by the same )}
%	\caption{Brillouin precursor propagation through tissue (reproduced from section 6).\\
%		(a) Gaussian monopulse with 16 ps FWHM.\\
%		(b) Optimized 10 GHz sawtooth wave. Note the slight high-frequency ripple.\\ This has a frequency of approximately 1.5 GHz.\\
%		(c) Prototypical precursor 10 GHz sine burst.\\
%		(d) Continuous 10 GHz sine tone.}
\end{figure}
\clearpage

@@

If the duration of exposure is sufficiently short that thermal and membrane breakdown effects can be neglected, tissue appears to withstand peak electric fields of great magnitude - above 1 nanosecond megavolt/meter, even in in-vivo studies - without severe acute effects(\cite{Repeated2020}\cite{Review2011} and below).

More specifically, the concept of driving a virus as a harmonic oscillator, as suggested by \cite{Efficient2015} has been previously considered only briefly \cite{MECHANICAL1968}\cite{Comment2004}\cite{Vibrational2009}\cite{Maximum2010}, perhaps first because in almost all cases structures in tissue are so over-damped by the surrounding solvent\cite{Vibrational2002}\cite{Biological2002}\cite{Biophysics2000}\cite{Viscous2000} as to have no non-zero resonant frequency at all \cite{dielectric1996}\cite{gabriel1996compilation}\wikinote{not in citation}\wikinote{discuss}; and second, because the charge distributions found in biology are too small for energies significantly above the thermal background to be absorbed via applied fields.

@@

Because the effect seen by\cite{Efficient2015} is so striking compared to previous work in the non-thermal literature, we have tried to invent ways of explaining the observed results without invoking a non-thermal effect. Sufficient orthogonal measurements were made, so this is quite difficult. The most plausible timeline was:
\begin{itemize}
	\item The use of microwave absorption spectroscopy techniques somewhat similar to those which have previously shown resonance-like artifacts\cite{Resonances1987}. In particular, an effective charge of $q=10^7 e^-$ was found via this method, which is very large for a $10^9$ atom structure.  Genome and protein charge can hardly explain $10^5 e^-$ (see below), which would be reduced further by ionic screening. It appears that the potential energy of such a sphere of charge would exceed the observed metabolic burden to build a virus by a significant factor \footnote{
		$$ U = \frac{3}{5}  \frac{1}{4 \pi \epsilon_0} \frac{Q^2}{R} \approx 2.3\text{e}^{-7} \text{ J} \approx 6 \times 10^{11}\  \text{ATP-equivalent} $$
		%U = (3/5) * 1/(4*pi*electricConstant) *((1e7 electricCharge)^2 / 60 nanometers) = 2.30708e-7 J

@@

	\item Infrared thermography only determines the surface temperature. Based on heating patterns seen in other experiments\cite{Effects1950}, the observed surface temperature rise does not seem to conclusively rule out a very localized thermal effect. 
	\item Therefore, without free-space dosimetry or simulation of power density to demonstrate otherwise, the frequency-selective inactivation could be explained by the frequency response of the power amplifier, antenna gain, and absorption of the cuvette.
\end{itemize}

It seems reasonable that a field with a strong positive publication bias\cite{Comprehensive2018}, in the presence of stringent peer review, might tend towards only the most abstruse and difficult to explain false-positive results.

@@

@@

With\footnote{The dipole spring constant can be extracted from the resonant frequency and therefore from the speed of sound and $m^*$, the reduced mass ($k = \omega_{res}^2 m^2$). } relatively sane choices of solvent charge screening and resonant frequency, the energy absorbed by the whole virus per cycle at 5 MV/m might vary from $10^{-5}$ to 100 times the thermal energy $k_b T$.
%TODO check effect of damping on hookes law energy.

Compare to $~5 k_b T$ per protein for 1 capsid segment binding energy \cite{Energies2012} \cite{Weak2002} and 6 to 30 $k_b T$ to form a single pore in a lipid bilayer \cite{Atomistic2014}.
%17 or 78 kJ/mol / (boltzmannConstant * 310 K) / avogadroConstant = 6.5 to 30.3 kT

@@

Poisson-Boltzmann implicit ionized solvents.

@@

\end{multicols}
\begin{figure}[H]
	%	\makebox[\textwidth][c]{
	\includesvg[width=\textwidth]{propagated_waveforms}
	\caption{Brillouin precursor propagation through tissue (reproduced from section 6).\\
		(a) Gaussian monopulse with 16 ps FWHM.\\
		(b) Optimized 10 GHz sawtooth wave. Note the slight high-frequency ripple.\\ This has a frequency of approximately 1.5 GHz.\\
		(c) Prototypical precursor 10 GHz sine burst.\\
		(d) Continuous 10 GHz sine tone.}

\end{figure}

\begin{multicols}{1}
Positive artifacts are very common in this field, and extreme care in experimental design appears to be required to produce any meaningful result. Excellent best-practices guidelines and meta-analyses are available in \cite{Biological2016} \cite{Comprehensive2018} \cite{Funding2019}, \cite{chou1996radio} and \cite{Effects2016}.

@@

A number of other capsid damage assays were evaluated. However, these initial tests were marred by the 1 uL sample volume in our initial cuvette attempts, our use of a domestic fridge to store phage, which unexpectedly froze regularly overnight, apparently reducing phage titer, along with our accidental use of T4r+ (not an "improved" T4r, as we believed, but rather a mutation away from rapid-lysis, meaning that the lysis behavior is far slower (see \cite{Spontaneous1946}). In our testing, lysis of T4r+ only occurred on plaque plates (where culture growth and log stage infectivity is maintained for many days)).

@@

E. coli produces the enzyme $\beta$-galactosidase to break lactose into glucose for metabolism. luciferase Promega Beta-Glo\cite{rapid2014}. However, one component contains a proprietary detergent designed to lyse cells and expose the galactosidase, counterproductive for phage use. Perhaps the detergent is not effective on bacteria, or the paper substrate that was used is sufficient. The detergent could perhaps be removed with BioBeads if this is desired.

While undoubtedly essential and very effective for its intended purpose (quantifying lac operon activity), because of ambiguities in the rise and decay of the luminescence signal, short shelf life when the two components are mixed, concerns regarding the detergent, and cost, Beta-Glo compared unfavorably to direct fluorescence or X-Gal for this application.

@@

A programmable syringe withdrew and pumped 50 uL of fluid at a constant rate through one of the coplanar channels, via a 4 cm long silicone capillary (McMaster-Carr \#51845K65) immersed in a 1.5 mL centrifuge tube using a 26 Ga Luer-lock (\#6710A76). Forcing phage through the capillary is similar to lysis with a French pressure cell press, but no such effects were seen.

@@

@@

	By using yet another exposure cell, introducing an new set of unknown artifacts, we hamper this field; and so we encourage anyone who may wish to persue similar results to not use this arrangement, but instead one of the existing, well-characterized exposure systems mentioned below or in the literature.

@@

Using Eppendorf tubes as. Impedimetric

Before the HMC732 was used, a misguided effort was spent in trying to develop an inexpensive wideband tunable oscillator.

Funded in part by the author's company, SafeSump Inc., and Ideal Consulting Inc., and the author's parents.

@@

Thanks to a group with Chengxiang Li for the Marx generator design we use in this paper. It is an excellent, very high performance design! Professor Shahramian's video blog informed this work, as did Dr. Dainis' on microbiology. Thanks to legend of dispersion himself, Professor Oughstun at Vermont, Prof. Sarris at U of Toronto, both for excellent information on optimal dispersive pulses; Professor Voinigescu at UofT for a tip on experiment engineering; Sandra and colleagues at York library for spending an hour looking for the Gray paper; Prof. Griffiths and Dr. Brovko at UGuelph and Dr. Anany at the GRDC for useful tips on the Beta-Glo assay; Professor Z-G Wang at Caltech for a note on viral electrostatics; Dr. James Hawthorne for the Autoleveller utility; Yuriy at Indiana; Barfuss for reviewing an early draft; Greenland Engineering for patience; and lots of friends - a few at York and many beyond.

@@

Hamming be damned; despite the name below the abstract, this paper is of course entirely the result of circumstance, luck, and awesome friends.

@@

Thanks to

One Very Important Thought

>>>>

\begin{figure}[H]
\captionsetup{singlelinecheck = false, justification=justified}
	\centering

	\subfloat[]{
		\includegraphics*[width=0.5\textwidth]{pulse_exposure_setup.JPG}

	}
	\subfloat[]{
		\includegraphics*[width=0.5\textwidth]{eppenwolf_output_cap.jpg}
	}
    \hfill
	\subfloat[]{
		\includegraphics*[width=0.5\textwidth]{bronch_9GHz_500W_2_transparent.png}
	}
	\subfloat[]{
		\includegraphics*[width=0.5\textwidth]{CPWG_sim_pretty_2}
	}
    \hfill

	\subfloat[]{
		\includegraphics[width=0.3\textwidth]{x_gal.jpg}
	}
	\subfloat[]{
		\includegraphics[width=0.5\textwidth]{fluro_1}
	}
%	\caption{Simulation of a (largely ineffective) bronchoscopic method.}

	\caption*{\small{\textit{Chengxiang} nanosecond pulse exposure jig. Aluminum disc belongs to the scan-conversion digitizer, not used in this study.}}
		\caption*{\small{Pulsed X-Band microwave spectrometer used in this study.}}
				\caption*{\small{FDTD simulation geometry of the 0.2 mm coplanar waveguide exposure cell. }}
						\caption*{\small{The very pretty opalescent blue culture caused by E. coli B and X-gal.}}
						\caption*{\small{Fluorescence reader used.}} 
%	\caption{Brillouin precursor propagation through tissue (reproduced from section 6).\\
%		(a) Gaussian monopulse with 16 ps FWHM.\\
%		(b) Optimized 10 GHz sawtooth wave. Note the slight high-frequency ripple.\\ This has a frequency of approximately 1.5 GHz.\\
%		(c) Prototypical precursor 10 GHz sine burst.\\
%		(d) Continuous 10 GHz sine tone.}
\end{figure}
\clearpage

@@

If the duration of exposure is sufficiently short that thermal and membrane breakdown effects can be neglected, tissue appears to withstand peak electric fields of great magnitude - above 1 nanosecond megavolt/meter, even in in-vivo studies - without severe acute effects (\cite{Repeated2020}\cite{Review2011}\cite{DNA2004} and below).

The specific concept of driving a virus as a harmonic oscillator suggested by \cite{Efficient2015} has been previously considered only briefly \cite{MECHANICAL1968}\cite{Comment2004}\cite{Vibrational2009}\cite{Maximum2010}\cite{Effects1951}, perhaps first because in almost all cases structures in tissue are so over-damped by the surrounding solvent\cite{Vibrational2002}\cite{Biological2002}\cite{Biophysics2000}\cite{Viscous2000} as to have no non-zero resonant frequency at all \cite{dielectric1996}\cite{gabriel1996compilation}\wikinote{not in citation}\wikinote{discuss}; and second, because the charge distributions found in biology are too small for energies significantly above the thermal background to be absorbed via applied fields.

@@

Because the effect seen by\cite{Efficient2015} is so striking compared to previous work in the non-thermal literature, we have tried to invent ways of explaining the observed results without invoking a non-thermal effect. Sufficient orthogonal measurements were made, so this is quite difficult. The most plausible timeline was:
\begin{itemize}
	\item The use of microwave absorption spectroscopy techniques somewhat similar to those which have previously shown resonance-like artifacts\cite{Resonances1987}. In particular, an effective charge of $q=10^7 e^-$ was found via this method, which seems quite large for a $10^9$ atom structure. Genome and protein charge can hardly explain $10^5 e^-$ (see below), which would be reduced further by ionic screening. It appears that the potential energy of such a sphere of charge would exceed the observed metabolic burden to build a virus by a significant factor \footnote{
		$$ U = \frac{3}{5}  \frac{1}{4 \pi \epsilon_0} \frac{Q^2}{R} \approx 2.3
		\times10^{-7} \text{ J} \approx 6 \times 10^{11}\  \text{ATP-equivalent} $$
		%U = (3/5) * 1/(4*pi*electricConstant) *((1e7 electricCharge)^2 / 60 nanometers) = 2.30708e-7 J

@@

	\item Infrared thermography only determines the surface temperature. Based on heating patterns seen in other experiments\cite{Effects1950}, the observed surface temperature rise does not seem to conclusively rule out a very localized thermal effect. 
	\item Therefore, without free-space dosimetry or simulation of power density, the frequency-selective inactivation could possibly be explained by the frequency response of the power amplifier, antenna gain, and absorption of the cuvette.
\end{itemize}

It seems reasonable that a field with a strong positive publication bias\cite{Comprehensive2018}, in the presence of stringent peer review, could tend towards only the most abstruse and difficult to explain false-positive results.

@@

Permeabilization at high field strengths is not necessarily completely implausible. \cite{182015} observe a similar non-ionic photoporation effect.

@@

With\footnote{The dipole spring constant can be extracted from the resonant frequency and therefore from the speed of sound and $m^*$, the reduced mass ($k = \omega_{res}^2 m^2$). } relatively sane choices of solvent charge screening and resonant frequency, the energy absorbed by the whole virus per cycle at 5 MV/m might vary from $10^{-5}$ to 100 times the thermal energy $k_b T$.

Compare to $~5 k_b T$ per protein for 1 capsid segment binding energy \cite{Energies2012} \cite{Weak2002} and 6 to 30 $k_b T$ to form a single pore in a lipid bilayer \cite{Atomistic2014}. \cite{Electrostatic2020a}
%17 or 78 kJ/mol / (boltzmannConstant * 310 K) / avogadroConstant = 6.5 to 30.3 kT

Brackley \cite{Electrostatic2020} describe various analytic representations of the charge screening about the virion with the Poisson-Boltzmann equation.

From a force perspective, the $10^3$ genome charge easily provides the nanonewton force scale required\cite{Bacteriophage2004} to break capsids or envelopes in 5 MV/m fields; but accurate estimation of the capsid stress will require application of the Maxwell stress tensor \cite{Electrostatic2013}\cite{Deformation1991}

@@

Coupling FEM \cite{Electrostatic2020a}.

@@

Positive artifacts are very common in this field, and extreme care in experimental design appears to be required to produce any meaningful result. Excellent best-practices guidelines and meta-analyses are available in \cite{Biological2016} \cite{Comprehensive2018} \cite{Funding2019}, \cite{chou1996radio} and \cite{Effects2016}.

@@

A number of other capsid damage assays were evaluated. However, these initial tests were marred by the 1 uL sample volume in our initial cuvette attempts, our use of a domestic fridge to store phage, which unexpectedly froze regularly overnight, apparently reducing phage titer, along with our accidental use of T4r+ (not an "improved" T4r, as we believed, but rather a mutation away from rapid-lysis, meaning that the lysis behavior is far slower (see \cite{Spontaneous1946}). In our testing, lysis of T4r+ only occurred on plaque plates [where culture growth and log stage infectivity is maintained for many days]).

@@

E. coli produces the enzyme $\beta$-galactosidase to break lactose into glucose for later metabolism. A luciferase-based luminescent assay, Promega Beta-Glo, was evaluated. One component of the beta-glo contains a proprietary detergent designed to lyse cells\cite{BETAGLO2003} and expose the enzyme, counterproductive for phage use. Perhaps the detergent is not effective on bacteria, or the paper substrate that w\cite{rapid2014}as used is sufficient. The detergent could perhaps be removed with BioBeads if this is desired.

While undoubtedly essential and very effective for its intended purpose (accurately quantifying lac operon activity), because of ambiguities in the rise and decay of the luminescence signal, short shelf life after the two components are mixed, oxygen depletion in small cuvettes, concerns regarding the detergent, and cost, Beta-Glo compared unfavorably to direct fluorescence or X-Gal for this application.

Positive control samples were put in a commercial pressure cooker to autoclave for either 6 or 20 minutes in an Eppendorf tube: the pressure was released after the cycle to prevent dilution. The flurophore was added after autoclaving.

@@

A programmable syringe withdrew and pumped 50 uL of fluid at a constant rate through one of the coplanar channels, via a 4 cm long silicone capillary (McMaster-Carr \#51845K65) immersed in a 1.5 mL centrifuge tube using a 26 Ga Luer-lock (\#6710A76). Forcing phage through the capillary is similar to lysis with a French pressure cell press, but no such effects were obviously seen.

@@

For the Eppenwolf, the lower bound is the lowest voltage measured on the diode detector through the sweep (at 12 GHz), (raw unconverted voltage across frequency can be seen at\ghfile{firmware/eppenwolf/runs/phage_experiment_12/screenshot_192.168.0.38_2020-11-26_13:38:24.png} - it is not recorded which detector this was seen at) multiplied by the FDTD results for the coplanar waveguide voltage to channel field scaling factor. The upper bound is the maximum voltage seen over the frequency sweep multiplied by the same FDTD factor.

\section{Discussion}

%For the pulser, the lower bound is

@@

	By using yet another exposure cell, introducing a new set of unknown artifacts, we hamper this field; and so we encourage anyone who may wish to persue similar results to not use this arrangement, but instead one of the existing, well-characterized exposure systems mentioned below or in the literature.

@@

Before the HMC732 was used, a misguided effort was spent in trying to develop an inexpensive wideband tunable oscillator for spectrometry. This will be chronicled in the GitHub repository.

\section{Acknowledgements}

Funded in part by the author's company, SafeSump Inc., and Ideal Consulting Inc., and the author's parents. The author was at YorkU for the duration of this project.

@@

Thanks to a group with Chengxiang Li for the Marx generator design we use in this paper. It is an excellent, very high performance design! Professor Shahramian's video blog informed this work, as did Dr. Dainis' on microbiology. Thanks to the legend of dispersion himself, Professor Oughstun at Vermont, Prof. Sarris at U of Toronto, both for excellent information on optimal dispersive pulses; Professor Voinigescu at UofT for a tip on experiment engineering; Sandra and colleagues at York library for spending an hour looking for the Gray paper; Prof. Griffiths and Dr. Brovko at UGuelph and Dr. Anany at the GRDC for useful tips on the Beta-Glo assay; Professor Z-G Wang at Caltech for a note on viral electrostatics; Dr. James Hawthorne for the Autoleveller utility; Yuriy at Indiana; Barfuss for reviewing an early draft; Greenland Engineering for patience; and lots of friends - a few at York and many beyond.

@@

Hamming was wrong; despite the name above the abstract, this paper is of course entirely the result of circumstance, luck, and awesome friends.

Special thanks to Alexandra Elbakyan and Aaron Swartz.

@@
